Reanalysis Step 3: Comprehensive Imputation Diagnostics

### 2025-08-30 reanalysis-3-imputation_diagnostics.qmd
clean up diagnsotics

temporal_summary <- temporal_df |>
  group_by(cohort_id) |>
  summarise(
    n = n(),
    mean_discrepancy = round(mean(discrepancy), 5),
    max_discrepancy = round(max(discrepancy), 5),
    pct_reversals = round(100 * mean(trajectory_reversal), 1),
    cor_segments = round(cor(change_1, change_2, use = "complete.obs"), 3),
    .groups = "drop"
  )

@@

# Sample trajectories
set.seed(2025)
sample_ids <- sample(temporal_df$row_number(), min(200, nrow(temporal_df)))

>>>>

temporal_summary <- temporal_df |>
  group_by(cohort_id) |>
  summarise(
    n = n(),
    mean_discrepancy = round(mean(discrepancy), 5),
    max_discrepancy = round(max(discrepancy), 5),
    pct_reversals = round(100 * mean(trajectory_reversal), 1),
    # Handle correlation when SD is zero (all values the same)
    cor_segments = if(sd(change_1, na.rm = TRUE) == 0 | sd(change_2, na.rm = TRUE) == 0) {
      NA_real_
    } else {
      round(cor(change_1, change_2, use = "complete.obs"), 3)
    },
    .groups = "drop"
  )

@@

# Sample trajectories
set.seed(2025)
n_sample <- min(200, nrow(temporal_df))
sample_ids <- sample(1:nrow(temporal_df), n_sample)
